%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Sr. Data Scientist} % Job title
    {CVS Health - Analytics \& Behavior Change} % Organization
    {Wellesley, MA} % Location
    {Aug. 2022 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {
        Implemented a BigQuery dataset with machine learning features supporting
        over \$100 MM of revenue through targeted member-level marketing
        materials and plan sponsor acquisition \& retention.
      }
      \item {
        Led technical design and implementation of a retrieval-assisted
        generative chat web application that indexed hundreds of unstructured
        documents (word, ppt, pdf) and assisted sales representatives
        responsible for accurately presenting and selling Aetna's products to
        its 14.5 million commercial members.
      }
      \item {
        Wrote and instructed an interactive ``Let's Git Going'' course for
        internal use that brought 50+ developers to a professional level using
        the Git version control system.
      }
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Sr. Data Scientist} % Job title
    {N1 Health (formerly Algorex Health Technologies)} % Organization
    {Boston, MA} % Location
    {Mar. 2021 - Aug. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {
        Principal developer of the internal Python software development kit,
        reducing the environment setup time from 45 minutes to 30 seconds and
        increasing net-new developer throughput by 50\%.
      }
      \item {
        Implemented automatic scaling and shutdown for data science
        architecture, saving \$40,000 annually and reducing on-boarding time
        from 3 days to 15 minutes.
      }
      \item {
        Led modeling of COVID-19 vaccine adoption rates for 3,500 vulnerable
        members around the greater Boston area, leading to targeted outreach
        recommendations.
      }
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Data Scientist (Pricing and Marketing)} % Job title
    {antuit.ai} % Organization
    {Frisco, TX} % Location
    {Sep. 2017 - Mar. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {
          Wrote an optimization algorithm for strategic pricing of consumer
          healthcare products in 11 countries, modeling more than \$5Bn in
          revenue across 8 product categories per country.
      }
      \item {
          Created ETL pipelines that prepared 1+ TB consumer healthcare
          product sales for a data warehouse.   I also designed over 50 custom
          views in the warehouse that reduced the average data scientist query
          time from 5 minutes to a few seconds and reduced the team's query
          costs by 80 percent.
      }
      % \item {
      %     Optimized MY2021 MSRP recommendations for an international motorcycle
      %     company, identifying opportunities targeting multiple strategic
      %     options - dealer revenue, manufacturer revenue/margin, or market
      %     penetration by motorcycle model. (Databricks, hyperopt)
      % }
      % \item {
      %     Modeled contractor costs for a warehouse trust fund and
      %     deployed the model/report into our client's
      %     infrastructure. (Denodo, Excel, Python)
      % }
      \item {
        Modeled customer churn and lifetime value for over 1 MM members for an
        international medical cosmetics provider.
      }
      \end{cvitems}
    }

\end{cventries}
